---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# easyplotP

<!-- badges: start -->
<!-- badges: end -->

The goal of easyplotP is to create a simple scatter plot using a set of numerical variables labelled x and y, to help visualize their relationship. A blue scatter plot is generated using this function.

## Installation

You can install the development version of easyplotP using:
[GitHub](https://github.com/) with:


``` r
#install.packages("devtools")
devtools::install_github("stat545ubc-2023/easyplotP", ref = "v0.1.13")

```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library("tidyverse")
library("ggplot2")
library("easyplotP")

data <- data.frame(A=c(0.4, 0.9, 1, 2, 7, 12, 44, 222), B=c(6, 8, 9, 10, 11, 18, 114, 1110))
easyplotP::easyplot(data$A, data$B)

```





